### 2025-03-02 mixed-models.qmd
20250302 - Bayesian model object

::: {#nte-bayesianMixedModel .callout-note title="Bayesian mixed model"}
Note: the following code takes a while to run.
:::

>>>>

::: {#nte-bayesianMixedModel .callout-note title="Bayesian mixed model"}
Note: the following code that runs the model takes a while.
If you just want to save time and load the model object instead of running the model, you can load the model object (which has already been fit) using this code:

```{r}
load(url("https://osf.io/download/q6rjf/"))
```
:::

### 2025-03-02 time-series-analysis.qmd
20250302 - Bayesian model object

```{r}
load(file = "./data/player_stats_weekly.RData")
load(file = "./data/player_stats_seasonal.RData")
load(url("https://osf.io/download/q6rjf/"))
```

>>>>

```{r}
load(file = "./data/player_stats_weekly.RData")
load(file = "./data/player_stats_seasonal.RData")
```

The following code loads the Bayesian model object that was fit in @sec-fantasyPointsByAgeExperienceModelsBayesian.

```{r}
load(url("https://osf.io/download/q6rjf/")) # Bayesian model object
```
